Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-13 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
Organize stereospecific Figure
Gnuplot script (gpl) and pdf output have been move the Fig folder.
A Makefile entry has been made to reproduce the figure
The tex source has been update with the new location
Two versions of dehydration plot.
Streamlined title.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[An \textsf{achemso} demo]
  {Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}}

@@

The most detailed experimentally available order parameter information for the glycerol backbone and choline 
segments of POPC bilayer is collected by taking the absolute values from~\cite{ferreira13}, the signs from~\cite{hong95a,hong95b,gross97} 
and the stereospecific labeling from~\cite{gally81}, and shown in Fig.~\ref{HGorderparameters2}.
\begin{figure*}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/stereospecificOPs.pdf} \\
  \caption{\label{HGorderparameters2}
  Order parameteres for POPC glycerol and choline groups
  from simulations with Berger-POPC-07, MacRog, GAFFlipid, and CHARMM36 force fields
  (the {\bf bolded} systems in Table~\ref{systems})
  together with experimental values.
  The error bars of simulation data are standard errors of mean (see Methods for details).
  The magnitudes for experimental order parameters are taken from Ferreira et al.~\cite{ferreira13},
  the signs are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
  and Gross et al.~\cite{gross97}, and the R/S labeling is based on the measurements by Gally et al.~\cite{gally81}.
}
\end{figure*}

@@

\subsubsection{Phospholipid bilayer with low hydration level}
The experimental order parameters available in the literature~\cite{dvinskikh05b,ulrich94,bechinger91} 
for the glycerol backbone and choline as a function of hydration level are shown in Fig.~\ref{ordPhydr}. 
The independently reported values for choline segments are in good agreement with each other (despite 
slight differences in temperature and acyl chain composition),
showing increase for both segments with decreasing hydration level. It should be noted that only 
absolute values were measured in the original experiments~\cite{dvinskikh05b,ulrich94,bechinger91}, but
we have included the signs measured in separate studies~\cite{hong95a,hong95b,gross97}. 
Consequently, the $\beta$ order parameter with negative sign actually increases with dehydration 
since the absolute value decreases~\cite{dvinskikh05b,ulrich94,bechinger91}.
Slight decrease for the glycerol backbone order parameters were observed with dehydration~\cite{dvinskikh05b}.
\begin{figure}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/dehydration.pdf} \\
    \caption{\label{ordPhydr}
    The effect of dehydration on glycerol and choline order parameters in experiments.
    The magnitudes of order parameters are measured for DMPC ($^1$H-$^{13}$C NMR) at 314~K~\cite{dvinskikh05b}, 
    for POPC ($^2$H NMR) at 296~K~\cite{bechinger91} and for DOPC ($^2$H NMR) at 303~K~\cite{ulrich94}. 
    The signs are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
    and Gross et al.~\cite{gross97}.
    Note that to elucidate the relative change as a function of hydration level,
    the simulation results are shifted such that the (smaller) $S_\mathrm{CH}$
    matches (within $\pm$0.01) the experimental value at full hydration;
    the shift magnitudes for each of the force fields are listed ($S_\mathrm{CH}$+shift) in the y-label.
  }
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[An \textsf{achemso} demo]
  {Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}}

@@

The most detailed experimentally available order parameter information for the glycerol backbone and choline 
segments of POPC bilayer is collected by taking the absolute values from~\cite{ferreira13}, the signs from~\cite{hong95a,hong95b,gross97} 
and the stereospecific labeling from~\cite{gally81}, and shown in Fig.~\ref{HGorderparameters2}.
\begin{figure*}[]
  \centering
  \includegraphics[width=8.6cm]{../Fig/stereospecificOPs.pdf} \\
  \caption{\label{HGorderparameters2}
  Order parameteres for POPC glycerol and choline groups
  from simulations with Berger-POPC-07, MacRog, GAFFlipid, and CHARMM36 force fields
  (the {\bf bolded} systems in Table~\ref{systems})
  together with experimental values.
  The error bars of simulation data are standard errors of mean (see Methods for details).
  The magnitudes for experimental order parameters are taken from Ferreira et al.~\cite{ferreira13},
  the signs are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
  and Gross et al.~\cite{gross97}, and the R/S labeling is based on the measurements by Gally et al.~\cite{gally81}.
}
\end{figure*}

@@

\subsubsection{Phospholipid bilayer with low hydration level}
The experimental order parameters available in the literature~\cite{dvinskikh05b,ulrich94,bechinger91} 
for the glycerol backbone and choline as a function of hydration level are shown in Fig.~\ref{ordPhydr}. 
The independently reported values for choline segments are in good agreement with each other (despite 
slight differences in temperature and acyl chain composition),
showing increase for both segments with decreasing hydration level. It should be noted that only 
absolute values were measured in the original experiments~\cite{dvinskikh05b,ulrich94,bechinger91}, but
we have included the signs measured in separate studies~\cite{hong95a,hong95b,gross97}. 
Consequently, the $\beta$ order parameter with negative sign actually increases with dehydration 
since the absolute value decreases~\cite{dvinskikh05b,ulrich94,bechinger91}.
Slight decrease for the glycerol backbone order parameters were observed with dehydration~\cite{dvinskikh05b}.
\begin{figure}[]
  \centering
  \includegraphics[width=7.3cm]{../DATAreportediINblog/dehydration_lp.pdf}
    \includegraphics[width=7.3cm]{../DATAreportediINblog/dehydration_smooth.pdf}
    \caption{\label{ordPhydr}
    The effect of dehydration on glycerol and choline order parameters in experiments.
    The magnitudes of order parameters are measured for DMPC ($^1$H-$^{13}$C NMR) at 314~K~\cite{dvinskikh05b}, 
    for POPC ($^2$H NMR) at 296~K~\cite{bechinger91} and for DOPC ($^2$H NMR) at 303~K~\cite{ulrich94}. 
    The signs are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
    and Gross et al.~\cite{gross97}.
    Note that to elucidate the relative change as a function of hydration level,
    the simulation results are shifted such that the (smaller) $S_\mathrm{CH}$
    matches (within $\pm$0.01) the experimental value at full hydration;
    the shift magnitudes for each of the force fields are listed ($S_\mathrm{CH}$+shift) in the y-label.
  }
  	\todo{Markus prepared two versions of this plot. The one on left has all the data points joint by lines;
	the one on right shows smooth trend lines (cubic polynomials) to ease qualitative comparison.
	Samuli likes the one on left, Markus the one on right. Do others have opinions?}
\end{figure}
